\section{Introduction}
Retrieval-augmented generation (RAG) conditions generation on external
documents, improving access to knowledge without encoding every fact in model
parameters \citep{lewis2020rag}. The same decomposition creates a debugging
problem. A wrong answer may follow from retrieval failure, evidence that is
present but misranked, a citation attached to the wrong source, an unsupported
answer extension, conflicting or stale sources, or a failure to abstain. A
single faithfulness score identifies none of these repair targets.

We study \emph{evidence-chain forensics}: reconstructing a verifiable path from
each answer claim through retrieved evidence and citation edges to an observable
failure and a concrete repair. This framing requires more than detecting
hallucination. It requires preserving intermediate decisions, refusing to
impute diagnostics a baseline does not expose, and distinguishing grounding in
supplied evidence from real-world truth.

\textsc{ContextTrace} implements this framing as a deterministic, local-first
pipeline. It consumes portable RAG or agent traces and emits claim verdicts,
minimal evidence spans, citation states, source assessments, abstention
decisions, failure labels, primary root causes, and evidence-backed repair and
regression suggestions. Figure~\ref{fig:pipeline} summarizes the pipeline.

Our contributions are: (1) a typed evidence-chain representation and diagnostic
contract; (2) a production-path benchmark protocol with same-ID comparisons,
case-bootstrap intervals, eleven registered ablation rows, and fail-closed claim
gates; (3) frozen pre-review results on ContextTrace-Diag-150 and a 200-case
RAGTruth sample; and (4) a preregistered human actionability protocol plus a
clearly separated 1,410-judgment LLM-simulated stress test. Independent human
review is pending, so we make dataset-specific pre-review claims only.
