\section{Related Work}
\paragraph{RAG evaluation.}
RAGAS decomposes automatic evaluation into faithfulness, answer relevance, and
context relevance \citep{es2024ragas}. ARES uses synthetic training data and
lightweight judges for context relevance, answer faithfulness, and answer
relevance \citep{saadfalcon2024ares}. DeepEval provides a software-oriented
collection of LLM evaluation metrics \citep{deepeval2026}. These tools make
automatic testing practical, but their outputs are not interchangeable with
root-cause, citation, and span diagnostics. Our baseline tables therefore score
only common outputs and mark unsupported fields N/A.

\paragraph{Diagnostic benchmarks.}
RAGChecker introduces fine-grained retriever and generator diagnostics
\citep{ru2024ragchecker}. RAGTruth supplies word-level hallucination annotations
across RAG tasks \citep{niu2024ragtruth}, while CRAG evaluates factual and
temporally dynamic retrieval settings \citep{yang2024crag}. ContextTrace uses
RAGTruth as external calibration evidence and CRAG as a secondary track; it
adds an explicit serialized chain from claims to repairs. The current external
annotations remain review-pending.

\paragraph{Model judges and observability.}
LLM judges can approximate human preferences \citep{zheng2023judge}, but order,
self-enhancement, and fairness biases remain material \citep{wang2024fair}. We
therefore report our model-based review solely as a simulated pilot. At the
systems layer, OpenTelemetry defines vendor-neutral trace concepts
\citep{opentelemetry2026}, and OpenInference extends semantic conventions to AI
workloads \citep{openinference2026}. ContextTrace accepts such trace-like
records but targets semantic evidence diagnosis rather than telemetry transport.
