\section{Benchmark Protocol}
We preregister case sets, profiles, seeds, metrics, and claim gates in a
machine-readable experiment specification. Prediction, scoring, review, and
claim authorization are separate stages (Figure~\ref{fig:protocol}). Every
bundle records case-ID hashes, candidate hashes, output hashes, dependency
versions, runtime, and reported cost.

\paragraph{Datasets.}
ContextTrace-Diag-150 contains 150 public-document traces covering support,
contradiction, abstention, citation, source, and root-cause behavior. The
external primary track is a deterministic 200-case sample derived from
RAGTruth \citep{niu2024ragtruth}. ARES and CRAG adapters provide secondary
calibration tracks. The 500-case engineering suite supports module regression
and ablation analysis; it is not independent validation.

\paragraph{Metrics.}
Primary detection uses failure-label macro-F1 and dangerous false-green rate,
where a false green is a trace with a material labeled failure that is reported
as clean. Diagnostic outputs use root-cause accuracy, citation-error F1, and
token-level evidence-span overlap. Claim-verdict macro-F1 is reported separately
because answer-level RAGTruth labels do not always determine an unambiguous
claim-level projection. We report deterministic 95\% case-bootstrap intervals
with 400 draws for the frozen experiment.

\paragraph{Review and claims.}
The reviewer packets hide predictions, expected labels, original IDs, and
private keys. Human sign-off is a distinct gate. Scored, assisted, or
LLM-simulated outputs cannot become ``independent'' through naming. The broad
claim gate validates bundle integrity, external coverage, review status,
thresholds, confidence intervals, same-ID competitor coverage, and Diag-150
sign-off. A single failed check blocks broad SOTA wording.

\input{figures/figure3_benchmark_protocol}
