\section{Error Analysis}
The frozen RAGTruth run contains nine primary failure-label misses and no
dangerous false greens under the current labels. Table~\ref{tab:table5-error-analysis}
separates observed clusters from categories that were not measured. Four clean
cases are overflagged, two contradictions are missed, and nine primary root
causes differ. The same-ID score-only baseline produces 60 dangerous false
greens. Span breadth, multi-span attribution, numeric/date normalization, and
stale-source behavior lack dedicated external tags and remain
\texttt{not\_measured}; judge parse failures are \texttt{not\_run}.

The simulated annotation stress test sharpens the uncertainty rather than
resolving it. Three agents disagree on 142 of 200 RAGTruth cases (Fleiss
$\kappa=0.033$) and 29 of 150 Diag cases ($\kappa=0.679$). Simulated majorities
disagree with 137 and 77 frozen labels respectively. All 214 suggestions remain
unapplied. Under a sensitivity-only replacement of those labels, combined
classification accuracy falls from 0.974 to 0.380 and macro-F1 from 0.978 to
0.139. This instability demonstrates why model consensus cannot be substituted
for independent adjudication.

The high RAGTruth failure score and low claim-verdict score also expose a scope
boundary: detecting an answer-level failure does not guarantee a correct
claim-by-claim decomposition. Final analysis will preserve raw reviewer
responses, report disagreements, and apply only separately versioned,
rationalized corrections.

\input{tables/table5_error_analysis}
